# R语言简介

关于编程，Jeremy Penzer写了一个guidlines，将其摘录如下：
> - **Problem specification**. This is the starting point for any program. Just as you would develop an objective and make an outline if you had to write a paper or report, rather than simply start writing, you should specify the problem as clearly as possible. Particularly important is determining what inputs your program needs and what outputs it should produce. It is also important to consider the problem and its solution from the perspective of those who will use the program and those who will benefit from
the solution.

> - **Code planning**. Contrary to what may be your notion of where to start, it is best not to start writing code, but rather to sketch out a rough version of the program with a pen and paper (or on a computer screen). If you know how to make a flow chart, that is a great idea too. Plan the code by making a nontechnical program prototype. Mock up the desired format of the output.

> - **Identify constants**. If you plan to use a constant or a variable, it is good to give that value an identifier at the beginning of the program. The advantage is obvious. If you assign a value to an argument or a constant, you can change that value once, and update all instances throughout the program.

> - **Program documentation**. Good programs are self-documenting. Lay out the code logically and clearly. Use spacing and indentation to make the code readable, and use comments to describe the complicated parts of your program. This helps you and others. When you comment the more complicated parts of your code, you will not have to remember weeks later what was very simple and obvious to you at the time, and you can sometimes spend hours deciphering your own “once-obvious” code. This is the voice of experience speaking here.

> - **Solve runtime problems**. Although books on programming are usually linear and straightforward, programming in real life is not like that at all. You may break your problem down into several steps, and work on them at different times. You will almost always find that your code does not produce the expected or desired results when you first execute it. You may or may not get much feedback about what went wrong.

> - **Verify your program**. As we are not developing large or sophisticated programs or functions, we are usually satisfied simply when we use some test cases for which we know the correct answers. More advanced forms of program verification are not needed in this case.

## 控制流 （Flow Control)

## 循环 (Looping)


## 协方差（covariance）和相关性（correlation）
我们想看两组数据是否独立，或者说想看两组数据是否相关。我们可以使用协方差:

$s_{xy}=\frac{\sum{(x-\bar{x})(y-\bar{y})}}{n-1}$

协方差的取值可以是正、0和负，如果值是正的，表明x和y的趋势一致，即x上升的话，y也是上升的。协方差的值受到x和y单位的影响，为了消除这一影响，将协方差除以x和y的标准差，我们得到的是相关系数。

```{r}
data(iris)
attach(iris)
cov(Sepal.Length, Sepal.Width)
cov(Sepal.Length, Sepal.Width)/(sd(Sepal.Length) * sd(Sepal.Width))
cor(Sepal.Length, Sepal.Width)
```

## 对称性度量
在使用参数检验之前需要度量我们的数据是否是对称分布的，通常使用偏度系数（skewness coefficient）和峰度系数（kurtosis coefficient)。根据定义，正态分布的偏度和峰度都为0。偏度系数计算的是三阶中心矩，而峰度系数计算的是四阶中心矩。

R并不提供函数度量偏度和峰度，这里使用*psych*包里的skew()和kurtosi()函数。
```{r}
library(psych)
skew(Sepal.Length)
```

